---
title: "ronxmaps: managing OnX Maps Markups from R"
author: "Robert Ritson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ronxmaps: managing OnX Maps Markups from R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(ronxmaps)
```

## Getting started
Here we are going to get started using the `ronxmaps` R package. Before you begin, you must have a valid OnX user account. "Hunt" accounts will likely  work best.

### Installation from GitHub (development version)

```{r install, include=TRUE,eval=F}
install.packages("remotes")
remotes::install_github("r2j2ritson/ronxmaps")
library(ronxmaps)
```


### Loging in to your OnX account
Run this in the console rather saving in a script in order to protect your account information. This information is stored in the system environment so you it can be discretely accessed when needed.
```{r login, include=T,eval=T}
ronxmaps::setCredentials(onx_email = "myonx_email@example.com",
                         onx_password = "myonxpassword")
```

You can check that your credential are correctly stored in the environment by running the following:
```{r view creds,include=T,eval=TRUE}
Sys.getenv('ONX_EMAIL')
Sys.getenv('ONX_PASSWORD')
```


```{r secret, include=F, eval=TRUE}
ronxmaps::setCredentials(onx_email = "robert.ritson@idfg.idaho.gov",
                         onx_password = "IDFG2020")
```


### Generate access token
Now that your information is discretely stored, you can then generate an access token for the OnX Web Maps API. This function can be re-run at anytime to generate a new access token or check how much more time is left on your current token. This may need to be repeated a few times before token is correctly acquired.
```{r token,include=TRUE,eval=T}
ronxmaps::getToken(onx_email = Sys.getenv('ONX_EMAIL'),
                   onx_password = Sys.getenv('ONX_PASSWORD'),
                   url = ronxmaps::onx_login_base(), 
                   verbose = T)
```


### View basic profile and subscription information
If successful, you should now be able to check your profile information to confirm you have access to the API.
```{r profile,include=T,eval=T}
ronxmaps::onx_subscriptions()
```

Congratulations! You officially have access to the OnX Maps Web API through R!

## Down to business: Managing your Markups!

### View Content
```{r profile,include=T,eval=T}
ronxmaps::onx_subscriptions()
```

### Save Content
```{r profile,include=T,eval=T}
ronxmaps::onx_subscriptions()
```

### Import Content
```{r profile,include=T,eval=T}
ronxmaps::onx_subscriptions()
```

### Delete Content
```{r profile,include=T,eval=T}
ronxmaps::onx_subscriptions()
```

### View folders
```{r profile,include=T,eval=T}
ronxmaps::onx_subscriptions()
```

### Delete folder
```{r profile,include=T,eval=T}
ronxmaps::onx_subscriptions()
```


## What's next?
