---
title: "ronxmaps: managing OnX Maps Markups from R"
author: "Robert Ritson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ronxmaps: managing OnX Maps Markups from R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(ronxmaps)
```

## Getting started
Here we are going to get started using the `ronxmaps` R package. Before you begin, you must have a valid OnX user account. "Hunt" accounts will likely  work best.

### Installation from GitHub (development version)

```{r install, include=TRUE,eval=F}
install.packages("remotes")
remotes::install_github("r2j2ritson/ronxmaps")
library(ronxmaps)
```


### Loging in to your OnX account
Run this in the console rather saving in a script in order to protect your account information. This information is stored in the system environment so you it can be discretely accessed when needed.
```{r login, include=T,eval=T}
ronxmaps::setCredentials(onx_email = "myonx_email@example.com",
                         onx_password = "myonxpassword")
```

You can check that your credential are correctly stored in the environment by running the following:
```{r view creds,include=T,eval=TRUE}
Sys.getenv('ONX_EMAIL')
Sys.getenv('ONX_PASSWORD')
```

### Generate access token
Now that your information is discretely stored, you can then generate an access token for the OnX Web Maps API. This function can be re-run at anytime to generate a new access token or check how much more time is left on your current token. This may need to be repeated a few times before token is correctly acquired.
```{r token,include=TRUE,eval=T}
ronxmaps::getToken(onx_email = Sys.getenv('ONX_EMAIL'),
                   onx_password = Sys.getenv('ONX_PASSWORD'),
                   url = ronxmaps::onx_login_base(), 
                   verbose = T)
```


### View basic profile and subscription information
If successful, you should now be able to check your profile information to confirm you have access to the API.
```{r profile,include=T,eval=T}
ronxmaps::onx_subscriptions()
```

Congratulations! You officially have access to the OnX Maps Web API through R!

## Down to business: Managing your Markups!

### View Content
```{r view pts,include=T,eval=T}
myPts <- ronxmaps::onx_list_markups(markup_type = "waypoints",parse=T)
head(myPts)
```

```{r view pts raw,include=T,eval=T}
myPts_raw <- ronxmaps::onx_list_markups(markup_type = "waypoints",parse=F)
myPts_raw[[100]]
```



```{r view track,include=T,eval=T}
myTracks <- ronxmaps::onx_list_markups(markup_type = "tracks",parse=T)
head(myTracks)
```

```{r view polys,include=T,eval=T}
myPolys <- ronxmaps::onx_list_markups(markup_type = "shapes",parse=T)
head(myPolys)
```

```{r plot markup interactive,include=T,eval=T}
ronxmaps::plot_markups(markup_type = "waypoints",interactive = T)
```

```{r plot markup,include=T,eval=T}
ronxmaps::plot_markups(markup_type = "tracks",interactive = F)
```

### Save Content
```{r convert to sf,include=T,eval=T}
polys_sf <- sf::st_as_sf(myPolys)
head(polys_sf)

plot(polys_sf[1,"geometry"])
```

```{r export markup,eval=F}
sf::st_write(polys_sf,"myOnXPolys.shp")
```

### Import Content
The package includes several internal files for testing uploads (a point `BorahPeak_kml`, a track `BorahPeakTrail_kml`, and a polygon`BorahPeakUSGSQuad_kml`).
```{r import markup,include=T,eval=F}
test_file <- ronxmaps::BorahPeak_kml
sf::st_write(test_file,"test_file.kml")
file <- file.path(getwd(),"test_file.kml")
import_kml2OnX(file = file, token = Sys.getenv("ONX_TOKEN", unset = ""))
```

### Delete Content
```{r delete markup,include=T,eval=F}
ronxmaps::delete_markup(myPolys$uuid[1])
```

### View folders
```{r view folder,include=T,eval=T}
folders <- ronxmaps::onx_content_collections(parse = T,include_entities = F)
head(folders)
```



## What's next?
